---
title: "Tabulating Results of Simulation Study"
author: "Michael Flanagin  \\ flanna@uw.edu"
date: "7/11/2018"
classoption: portrait
header-includes:
  - \usepackage[table]{xcolor}
  - \usepackage{booktabs}
  - \usepackage{caption}
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
  html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    theme: cerulean
csl: mee.csl
bibliography: references.bib
---
\captionsetup[table]{ labelformat = empty } <!-- disable auto table numbering with kable -->

```{r setup, eval = FALSE, echo=FALSE}
  devtools::install_github("cboettig/knitcitations@v1")
  library(knitcitations); cleanbib()
  cite_options(citation_format = "pandoc", check.entries=FALSE)
  library(bibtex)
```

```{r globalopts, cache = TRUE, warning = FALSE, echo = FALSE}
# Load libraries necessary for functions used in this document
library('knitr')
library('xtable')
library('kableExtra')  # for additional table formatting
# library('dplyr')  # for table coloring
# Set global chunk options
opts_chunk$set(echo = FALSE,     # do NOT repeat code in final document
               message = FALSE,  # do NOT print R messages in document
               warning = FALSE,  # do NOT print warnings
               self.contained = TRUE ) # do NOT call other .Rnw docs! 
round_digits <- 3  # digits to round to when presenting results
options( knitr.table.format = "latex")  # guarantees 'kableExtra' formatting handled properly
options( scipen = 999 )
#         knitr.kable.na = " - ", 
#         scipen = 10)  # replaces NA entries with ' - ' in kable output
#         scipen = 999 )  # effectively disables scientific notation
setwd(getwd())  # set working directory to current file path.

# function kable_booktabs_linesep()
kable_booktabs_linesep <- function( nlines = 6 ){
  #' input: 
  #'   nlines := number of lines per block of table rows
  #' output:
  #'   [character] linespace string to pass to kable()
  #' example:
  #'   kable( foo_table, booktabs = TRUE, linesep = kable_booktabs_linesep( nlines = 6) )
  return(c(rep( '', nlines - 1 ), "\\addlinespace"))
}
```

```{r load_datasets, cache = TRUE, echo = FALSE}
datadir_path <- "/Users/Moschops/Documents/MSThesis/results/"
#' [ Batch 1 of 4: binary Y, binary X ] 
metrics_bybx <- read.csv(paste0( datadir_path, "metrics-alloc-simulation-batch-1-of-4.csv" ))
#' [ Batch 2 of 4: binary Y, continuous X ] 
metrics_bycx <- read.csv(paste0( datadir_path, "metrics-alloc-simulation-batch-2-of-4.csv" ))
#' [ Batch 3 of 4: continuous Y, binary X ] 
metrics_cybx <- read.csv(paste0( datadir_path, "metrics-alloc-simulation-batch-3-of-4.csv" ))
#' [ Batch 4 of 4: continuous Y, continuous X ] 
metrics_cycx <- read.csv(paste0( datadir_path, "metrics-alloc-simulation-batch-4-of-4.csv" ))

datadir_path_new <- "/Users/Moschops/Documents/MSThesis/results-NEW/"
#' [ Batch 1 of 4: binary Y, binary X -- subsetted on simulations without complete/quasi separation ]
metrics_bybx_sub <- read.csv(paste0( datadir_path, "metrics-subset-alloc-simulation-batch-1-of-4.csv" ))
#' [ Batch 2 of 4: binary Y, continuous X -- subsetted on simulations without complete/quasi separation ]
metrics_bycx_sub <- read.csv(paste0( datadir_path, "metrics-subset-alloc-simulation-batch-2-of-4.csv" ))


#' [ Batch 1 of 4: binary Y, binary X -- subsetted on simulations without complete/quasi separation ]
metrics_bybx_sub_new <- read.csv(paste0( datadir_path_new, "metrics-subset-alloc-simulation-batch-1-of-4.csv" ))
#' [ Batch 2 of 4: binary Y, continuous X -- subsetted on simulations without complete/quasi separation ]
metrics_bycx_sub_new <- read.csv(paste0( datadir_path_new, "metrics-subset-alloc-simulation-batch-2-of-4.csv" ))

with( metrics_bybx, summary( bias ))
with( metrics_bybx_sub, summary( bias ))
with( metrics_bybx_sub_new, summary( bias ))
with( metrics_bycx, summary( bias ))
with( metrics_bycx_sub, summary( bias ))
with( metrics_bycx_sub_new, summary( bias ))


```

# Introduction
Simulation results are presented by outcome and predictor variable type pairs (binary, continuous).

Each outcome/predictor pair, we present tables on: 

* coverage probability, 
* bias, and 
* power.

Simulation conditions are ordered by:

* sample size (n), 
* marginal outcome prevalence Pr( Y ),
* prognostic factor prevalence Pr( X ),
* treatment effect size (exp( bZ )), and
* prognostic factor effect size (bX).

Binary outcomes are fit with a Binomial generalized linear model, continuous outomes with an ordinary linear model.

Resulting estimates of treatment effect are adjusted ('adj') or unadjusted ('unadj') for prognostic factors used in the allocation method.

Three allocation methods are compared to each other:

* Complete randomization (CR),
* Stratified block randomization (SBR), with a block size of 4,
* Covariate adaptive allocation (CAA), with a maximum imbalance of 2 and an allocation biasing probability of 0.70.

The analysis method for uncertainty estimates is either:

* Model-based (using p-values from relevant t-statistics), or
* Rerandomization-based, with 500 rerandomized treatment allocations performed per simulation draw.

# Comments
Suggested modifications:

* Order simulation conditions in sort order, i.e. columns from left to right should go: n, Pr(Y), Pr(X), ...
* Investigate issue with large positive biases
* Correct issue with scientific notation (suspect it may have to do with high bias (see previous)
* For batches 1 and 2, present complete and subsetted metric table side by side / sequentially (rather than currently: complete results, then subsetted results)
\newpage

# Comments from Amalia (NEW: 18 July 2018)

OK, fantastic, here are some thoughts on this version.  Try to refer to this email as a checklist and go through each one.

For formatting,

1. Number the tables based on batch number (1a 1b, etc) so can tell where you are in the types of outcomes.

ref1: https://stackoverflow.com/questions/31182147/suppress-automatic-table-name-and-number-in-an-rmd-file-using-xtable-or-knitr
ref2: https://stackoverflow.com/questions/30679537/get-rid-of-captions-when-using-texreg-in-rmarkdown
```
In the YAML section where LaTeX packages can be included, 
add the caption package:

header-includes:
    - \usepackage{caption}
Then at the beginning of the RMarkdown document body add:

\captionsetup[table]{labelformat=empty}
This removes the caption labels for all tables.
```

2. Include the proportion of runs included in each row of the tables where you include only simulations without non-complete separation

3. Some tables still need scientific notation taken out of the extra large or small numbers.  If #s too big, perhaps can use >999 or something

4. I like the row spacing used to split up the vertical space, you have used every 5 rows, but perhaps split where something changes to make more coherent groups, perhaps every 6 rows where the value of P(X) or P(Y) changes.  Even batch 4 could put a vertical space every 6 rows since sample size changes.

```
You can add the argument linesep = "" to kable. 
This will be passed on to kable_latex where it overwrites the default

linesep = if (booktabs) c('', '', '', '', '\\addlinespace') else '\\hline'
# Example:

kable(cars, format = "latex", booktabs = TRUE, linesep = "")
```
Made a function that outputs a formatted string for 'linesep' argument, with the given number of lines per separation:
```{r}
# function kable_booktabs_linesep()
kable_booktabs_linesep <- function( nlines = 6 ){
  #' input: 
  #'   nlines := number of lines per block of table rows
  #' output:
  #'   [character] linespace string to pass to kable()
  #' example:
  #'   kable( foo_table, booktabs = TRUE, linesep = kable_booktabs_linesep( nlines = 6) )
  return(c(rep( '', nlines - 1 ), "\\addlinespace"))
}
```

5. Sometimes the columns at the right have NA and sometimes just 0 or 1.  I’m assuming when it’s just 0 or 1 that those have not finished running yet, right?

6. Remove far right column for rerandomized and unadjusted.  Do not run these, not part of our aims.

7. Something seems amiss with table 11, some of the columns match exactly.

8. Tables 11 and 12 both say ‘bias’ in heading, but I think second one should be power?


For inference,

9. We need to be able to interpret the bias.  So each table should include the true value that was compared to the estimates to compute bias.  I think when we sat down this was log(bZ), not bZ, right? 

10. Here is what I’m seeing in terms of patterns:  Coverage and bias seem potentially reasonable, waiting for some precision, hard to see. 

11. So focusing on power, which is our main objective.  Seems to me that there is actually a benefit in terms of power for re-randomization even in the absence of drift for binary Y; this is seen when comparing CAA rerand adj vs CAA model-based adj. 

12. Secondly with regard to power, when comparing the model based adjusted methods only and ignoring rerandomization, there seems to be no power advantage to using covariate adjusted randomization versus either block or simple randomization.  Do you agree?  Fascinating.

13. How it is going with the other simulations not shown here, batches 1 and 2 with n=96?  Are they running?






<!-- # Batch 1: Binary outcome (Y), binary prognostic factors (X) {-} -->
```{r batch-1-binY-binX_coverage, cache = TRUE, echo = FALSE}
#' Adjusted analysis
tbl11_cov_adj <- subset( metrics_bybx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 1 ) )
tbl12_cov_adj <- subset( metrics_bybx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 1 ) )
tbl13_cov_adj <- subset( metrics_bybx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 1 ) )
tbl14_cov_adj <- subset( metrics_bybx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 1 ) )
#' Unadjusted analysis
tbl11_cov_un <- subset( metrics_bybx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 0 ) )
tbl12_cov_un <- subset( metrics_bybx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 0 ) )
tbl13_cov_un <- subset( metrics_bybx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 0 ) )
tbl14_cov_un <- subset( metrics_bybx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 0 ) )

#' Table 1a: Coverage (adjusted tx effect)
tbl1_coverage_adj <- cbind( CR = round( tbl11_cov_adj[,"coverage"], round_digits ),
                            SBR = round( tbl12_cov_adj[,"coverage"], round_digits ),
                            CAA_model = round( tbl13_cov_adj[,"coverage"], round_digits ),
                            CAA_rerand = round( tbl14_cov_adj[,"coverage"], round_digits ),
                            tbl13_cov_adj[,-1] )
dimnames( tbl1_coverage_adj )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )", "Pr( X )")

#' Table 1b: Coverage (adjusted tx effect)
tbl1_coverage_un <- cbind( CR = round( tbl11_cov_un[,"coverage"], round_digits ),
                            SBR = round( tbl12_cov_un[,"coverage"], round_digits ),
                            CAA_model = round( tbl13_cov_un[,"coverage"], round_digits ),
                           CAA_rerand = rep(NA, times = nrow( tbl14_cov_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                             CAA_rerand = round( tbl14_cov_un[,"coverage"], round_digits ),
                            tbl13_cov_un[,-1] )
dimnames( tbl1_coverage_un )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )", "Pr( X )")
```

```{r batch-1-binY-binX_bias, cache = TRUE, echo = FALSE}
#' Adjusted analysis
tbl11_bias_adj <- subset( metrics_bybx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 1 ) )
tbl12_bias_adj <- subset( metrics_bybx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 1 ) )
tbl13_bias_adj <- subset( metrics_bybx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 1 ) )
tbl14_bias_adj <- subset( metrics_bybx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 1 ) )
#' Unadjusted analysis
tbl11_bias_un <- subset( metrics_bybx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 0 ) )
tbl12_bias_un <- subset( metrics_bybx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 0 ) )
tbl13_bias_un <- subset( metrics_bybx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 0 ) )
tbl14_bias_un <- subset( metrics_bybx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 0 ) )

#' Table 1a: Coverage (adjusted tx effect)
tbl1_bias_adj <- cbind( CR = round( tbl11_bias_adj[,"bias"], round_digits ),
                            SBR = round( tbl12_bias_adj[,"bias"], round_digits ),
                            CAA_model = round( tbl13_bias_adj[,"bias"], round_digits ),
                            CAA_rerand = round( tbl14_bias_adj[,"bias"], round_digits ),
                            tbl13_bias_adj[,-1] )
dimnames( tbl1_bias_adj )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )", "Pr( X )")

#' Table 1b: Coverage (adjusted tx effect)
tbl1_bias_un <- cbind( CR = round( tbl11_bias_un[,"bias"], round_digits ),
                            SBR = round( tbl12_bias_un[,"bias"], round_digits ),
                            CAA_model = round( tbl13_bias_un[,"bias"], round_digits ),
                           CAA_rerand = rep(NA, times = nrow( tbl14_bias_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                             CAA_rerand = round( tbl14_bias_un[,"bias"], round_digits ),
                            tbl13_bias_un[,-1] )
dimnames( tbl1_bias_un )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )", "Pr( X )")
```

```{r batch-1-binY-binX_power, cache = TRUE, echo = FALSE}
#' Adjusted analysis
tbl11_power_adj <- subset( metrics_bybx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 1 ) )
tbl12_power_adj <- subset( metrics_bybx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 1 ) )
tbl13_power_adj <- subset( metrics_bybx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 1 ) )
tbl14_power_adj <- subset( metrics_bybx, select = c( power.rerand, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 1 ) )
#' Unadjusted analysis
tbl11_power_un <- subset( metrics_bybx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 0 ) )
tbl12_power_un <- subset( metrics_bybx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 0 ) )
tbl13_power_un <- subset( metrics_bybx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 0 ) )
tbl14_power_un <- subset( metrics_bybx, select = c( power.rerand, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 0 ) )

#' Table 1a: Coverage (adjusted tx effect)
tbl1_power_adj <- cbind( CR = round( tbl11_power_adj[,"power.pvalue"], round_digits ),
                            SBR = round( tbl12_power_adj[,"power.pvalue"], round_digits ),
                            CAA_model = round( tbl13_power_adj[,"power.pvalue"], round_digits ),
                            CAA_rerand = round( tbl14_power_adj[,"power.rerand"], round_digits ),
                            tbl13_power_adj[,-1] )
dimnames( tbl1_power_adj )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )", "Pr( X )")

#' Table 1b: Coverage (adjusted tx effect)
tbl1_power_un <- cbind( CR = round( tbl11_power_un[,"power.pvalue"], round_digits ),
                            SBR = round( tbl12_power_un[,"power.pvalue"], round_digits ),
                            CAA_model = round( tbl13_power_un[,"power.pvalue"], round_digits ),
                           CAA_rerand = rep(NA, times = nrow( tbl14_power_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                             CAA_rerand = round( tbl14_power_un[,"power.rerand"], round_digits ),
                            tbl13_power_un[,-1] )
dimnames( tbl1_power_un )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )", "Pr( X )")
```

```{r batch-1-sort-subset, cache = TRUE, echo = FALSE}
# Remove single n = 96 case:
tbl1_coverage_adjsub <- subset( tbl1_coverage_adj, n == 32 )
tbl1_coverage_unsub <- subset( tbl1_coverage_un, n == 32 )
tbl1_bias_adjsub <- subset( tbl1_bias_adj, n == 32 )
tbl1_bias_unsub <- subset( tbl1_bias_un, n == 32 )
tbl1_power_adjsub <- subset( tbl1_power_adj, n == 32 )
tbl1_power_unsub <- subset( tbl1_power_un, n == 32 )
# Ordering by $p(Y), p(X), \beta_Z, \beta_X$:
tbl1_coverage_adj_sort <- tbl1_coverage_adjsub[ do.call( order, tbl1_coverage_adjsub[,c(5, 8, 9, 6, 7)] ), ]
tbl1_coverage_un_sort <- tbl1_coverage_unsub[ do.call( order, tbl1_coverage_unsub[,c(5, 8, 9, 6, 7)] ), ]
tbl1_bias_adj_sort <- tbl1_bias_adjsub[ do.call( order, tbl1_bias_adjsub[,c(5, 8, 9, 6, 7)] ), ]
tbl1_bias_un_sort <- tbl1_bias_unsub[ do.call( order, tbl1_bias_unsub[,c(5, 8, 9, 6, 7)] ), ]
tbl1_power_adj_sort <- tbl1_power_adjsub[ do.call( order, tbl1_power_adjsub[,c(5, 8, 9, 6, 7)] ), ]
tbl1_power_un_sort <- tbl1_power_unsub[ do.call( order, tbl1_power_unsub[,c(5, 8, 9, 6, 7)] ), ]
```

```{r batch-1-adj-unadj-tables, cache = TRUE, echo = FALSE}
tbl1_coverage <- cbind( tbl1_coverage_adj_sort[,c(5:9)],
                        CR_adj = tbl1_coverage_adj_sort[, "CR"],
                        CR_un = tbl1_coverage_un_sort[, "CR"],
                        SBR_adj = tbl1_coverage_adj_sort[, "SBR"],
                        SBR_un = tbl1_coverage_un_sort[, "SBR"],
                        CAA_model_adj = tbl1_coverage_adj_sort[, "CAA_model"],
                        CAA_model_un = tbl1_coverage_un_sort[, "CAA_model"],
                        CAA_rerand_adj = tbl1_coverage_adj_sort[, "CAA_rerand"],
                        CAA_rerand_un = tbl1_coverage_un_sort[, "CAA_rerand"])

tbl1_bias <- cbind( tbl1_bias_adj_sort[,c(5:9)],
                        CR_adj = tbl1_bias_adj_sort[, "CR"],
                        CR_un = tbl1_bias_un_sort[, "CR"],
                        SBR_adj = tbl1_bias_adj_sort[, "SBR"],
                        SBR_un = tbl1_bias_un_sort[, "SBR"],
                        CAA_model_adj = tbl1_bias_adj_sort[, "CAA_model"],
                        CAA_model_un = tbl1_bias_un_sort[, "CAA_model"],
                        CAA_rerand_adj = tbl1_bias_adj_sort[, "CAA_rerand"],
                        CAA_rerand_un = tbl1_bias_un_sort[, "CAA_rerand"])

tbl1_power <- cbind( tbl1_power_adj_sort[,c(5:9)],
                        CR_adj = tbl1_power_adj_sort[, "CR"],
                        CR_un = tbl1_power_un_sort[, "CR"],
                        SBR_adj = tbl1_power_adj_sort[, "SBR"],
                        SBR_un = tbl1_power_un_sort[, "SBR"],
                        CAA_model_adj = tbl1_power_adj_sort[, "CAA_model"],
                        CAA_model_un = tbl1_power_un_sort[, "CAA_model"],
                        CAA_rerand_adj = tbl1_power_adj_sort[, "CAA_rerand"],
                        CAA_rerand_un = tbl1_power_un_sort[, "CAA_rerand"])
```

<!-- BATCH 1 of 4, SUBSETTING ON VALID simulations --> 
```{r batch-1-subset-binY-binX_coverage, cache = TRUE, echo = FALSE}
#' Adjusted analysis
tbl1sub1_cov_adj <- subset( metrics_bybx_sub, select = c( nsim, coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 1 ) )
tbl1sub2_cov_adj <- subset( metrics_bybx_sub, select = c( nsim, coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 1 ) )
tbl1sub3_cov_adj <- subset( metrics_bybx_sub, select = c( nsim, coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 1 ) )
tbl1sub4_cov_adj <- subset( metrics_bybx_sub, select = c( nsim, coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 1 ) )
#' Unadjusted analysis
tbl1sub1_cov_un <- subset( metrics_bybx_sub, select = c( nsim, coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 0 ) )
tbl1sub2_cov_un <- subset( metrics_bybx_sub, select = c( nsim, coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 0 ) )
tbl1sub3_cov_un <- subset( metrics_bybx_sub, select = c( nsim, coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 0 ) )
tbl1sub4_cov_un <- subset( metrics_bybx_sub, select = c( nsim, coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 0 ) )

#' Table 1a: Coverage (adjusted tx effect)
index_remove <- which( colnames(tbl1sub3_cov_adj) == "coverage" )
tbl1sub_coverage_adj <- cbind( CR = round( tbl1sub1_cov_adj[,"coverage"], round_digits ),
                            SBR = round( tbl1sub2_cov_adj[,"coverage"], round_digits ),
                            CAA_model = round( tbl1sub3_cov_adj[,"coverage"], round_digits ),
                            CAA_rerand = round( tbl1sub4_cov_adj[,"coverage"], round_digits ),
                            tbl1sub3_cov_adj[, -index_remove] )
dimnames( tbl1sub_coverage_adj )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )", "Pr( X )")

#' Table 1b: Coverage (adjusted tx effect)
index_remove <- which( colnames(tbl1sub3_cov_un) == "coverage" )

tbl1sub_coverage_un <- cbind( CR = round( tbl1sub1_cov_un[,"coverage"], round_digits ),
                            SBR = round( tbl1sub2_cov_un[,"coverage"], round_digits ),
                            CAA_model = round( tbl1sub3_cov_un[,"coverage"], round_digits ),
                           CAA_rerand = rep(NA, times = nrow( tbl1sub4_cov_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                             CAA_rerand = round( tbl1sub4_cov_un[,"coverage"], round_digits ),
                            tbl1sub3_cov_un[,-index_remove] )
dimnames( tbl1sub_coverage_un )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )", "Pr( X )")
```

```{r batch-1-subset-binY-binX_bias, cache = TRUE, echo = FALSE}
#' Adjusted analysis
tbl1sub1_bias_adj <- subset( metrics_bybx_sub, select = c( nsim, bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 1 ) )
tbl1sub2_bias_adj <- subset( metrics_bybx_sub, select = c( nsim, bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 1 ) )
tbl1sub3_bias_adj <- subset( metrics_bybx_sub, select = c( nsim, bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 1 ) )
tbl1sub4_bias_adj <- subset( metrics_bybx_sub, select = c( nsim, bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 1 ) )
#' Unadjusted analysis
tbl1sub1_bias_un <- subset( metrics_bybx_sub, select = c( nsim, bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 0 ) )
tbl1sub2_bias_un <- subset( metrics_bybx_sub, select = c( nsim, bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 0 ) )
tbl1sub3_bias_un <- subset( metrics_bybx_sub, select = c( nsim, bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 0 ) )
tbl1sub4_bias_un <- subset( metrics_bybx_sub, select = c( nsim, bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 0 ) )

#' Table 1a: Coverage (adjusted tx effect)
index_remove <- which( colnames(tbl1sub3_bias_adj) == "bias" )
tbl1sub_bias_adj <- cbind( CR = round( tbl1sub1_bias_adj[,"bias"], round_digits ),
                            SBR = round( tbl1sub2_bias_adj[,"bias"], round_digits ),
                            CAA_model = round( tbl1sub3_bias_adj[,"bias"], round_digits ),
                            CAA_rerand = round( tbl1sub4_bias_adj[,"bias"], round_digits ),
                            tbl1sub3_bias_adj[,-index_remove] )
dimnames( tbl1sub_bias_adj )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )", "Pr( X )")

#' Table 1b: Coverage (adjusted tx effect)
index_remove <- which( colnames(tbl1sub3_bias_adj) == "bias" )
tbl1sub_bias_un <- cbind( CR = round( tbl1sub1_bias_un[,"bias"], round_digits ),
                            SBR = round( tbl1sub2_bias_un[,"bias"], round_digits ),
                            CAA_model = round( tbl1sub3_bias_un[,"bias"], round_digits ),
                           CAA_rerand = rep(NA, times = nrow( tbl1sub4_bias_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                             CAA_rerand = round( tbl1sub4_bias_un[,"bias"], round_digits ),
                            tbl1sub3_bias_adj[,-index_remove] )
dimnames( tbl1sub_bias_un )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )", "Pr( X )")
```

```{r batch-1-subset-binY-binX_power, cache = TRUE, echo = FALSE}
#' Adjusted analysis
tbl1sub1_power_adj <- subset( metrics_bybx_sub, select = c( nsim, power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 1 ) )
tbl1sub2_power_adj <- subset( metrics_bybx_sub, select = c( nsim, power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 1 ) )
tbl1sub3_power_adj <- subset( metrics_bybx_sub, select = c( nsim, power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 1 ) )
tbl1sub4_power_adj <- subset( metrics_bybx_sub, select = c( nsim, power.rerand, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 1 ) )
#' Unadjusted analysis
tbl1sub1_power_un <- subset( metrics_bybx_sub, select = c( nsim, power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 0 ) )
tbl1sub2_power_un <- subset( metrics_bybx_sub, select = c( nsim, power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 0 ) )
tbl1sub3_power_un <- subset( metrics_bybx_sub, select = c( nsim, power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 0 ) )
tbl1sub4_power_un <- subset( metrics_bybx_sub, select = c( nsim, power.rerand, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 0 ) )

#' Table 1a: Coverage (adjusted tx effect)
# TODO(michael): fix 'index_remove' for all cases where 'nsim' is added!
tbl1sub_power_adj <- cbind( CR = round( tbl1sub1_power_adj[,"power.pvalue"], round_digits ),
                            SBR = round( tbl1sub2_power_adj[,"power.pvalue"], round_digits ),
                            CAA_model = round( tbl1sub3_power_adj[,"power.pvalue"], round_digits ),
                            CAA_rerand = round( tbl1sub4_power_adj[,"power.rerand"], round_digits ),
                            tbl1sub3_power_adj[,-index_remove] )
dimnames( tbl1sub_power_adj )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )", "Pr( X )")

#' Table 1b: Coverage (adjusted tx effect)
tbl1sub_power_un <- cbind( CR = round( tbl1sub1_power_un[,"power.pvalue"], round_digits ),
                            SBR = round( tbl1sub2_power_un[,"power.pvalue"], round_digits ),
                            CAA_model = round( tbl1sub3_power_un[,"power.pvalue"], round_digits ),
                           CAA_rerand = rep(NA, times = nrow( tbl1sub4_power_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                             CAA_rerand = round( tbl1sub4_power_un[,"power.rerand"], round_digits ),
                            tbl1sub3_power_un[,-1] )
dimnames( tbl1sub_power_un )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )", "Pr( X )")
```

```{r batch-1-subset-sort-subset, cache = TRUE, echo = FALSE}
# Remove single n = 96 case:
tbl1sub_coverage_adjsub <- subset( tbl1sub_coverage_adj, n == 32 )
tbl1sub_coverage_unsub <- subset( tbl1sub_coverage_un, n == 32 )
tbl1sub_bias_adjsub <- subset( tbl1sub_bias_adj, n == 32 )
tbl1sub_bias_unsub <- subset( tbl1sub_bias_un, n == 32 )
tbl1sub_power_adjsub <- subset( tbl1sub_power_adj, n == 32 )
tbl1sub_power_unsub <- subset( tbl1sub_power_un, n == 32 )
# Ordering by $p(Y), p(X), \beta_Z, \beta_X$:
tbl1sub_coverage_adj_sort <- tbl1sub_coverage_adjsub[ do.call( order, tbl1sub_coverage_adjsub[,c(5, 8, 9, 6, 7)] ), ]
tbl1sub_coverage_un_sort <- tbl1sub_coverage_unsub[ do.call( order, tbl1sub_coverage_unsub[,c(5, 8, 9, 6, 7)] ), ]
tbl1sub_bias_adj_sort <- tbl1sub_bias_adjsub[ do.call( order, tbl1sub_bias_adjsub[,c(5, 8, 9, 6, 7)] ), ]
tbl1sub_bias_un_sort <- tbl1sub_bias_unsub[ do.call( order, tbl1sub_bias_unsub[,c(5, 8, 9, 6, 7)] ), ]
tbl1sub_power_adj_sort <- tbl1sub_power_adjsub[ do.call( order, tbl1sub_power_adjsub[,c(5, 8, 9, 6, 7)] ), ]
tbl1sub_power_un_sort <- tbl1sub_power_unsub[ do.call( order, tbl1sub_power_unsub[,c(5, 8, 9, 6, 7)] ), ]
```

```{r batch-1-subset-adj-unadj-tables, cache = TRUE, echo = FALSE}
tbl1sub_coverage <- cbind( tbl1sub_coverage_adj_sort[,c(5:9)],
                        CR_adj = tbl1sub_coverage_adj_sort[, "CR"],
                        CR_un = tbl1sub_coverage_un_sort[, "CR"],
                        SBR_adj = tbl1sub_coverage_adj_sort[, "SBR"],
                        SBR_un = tbl1sub_coverage_un_sort[, "SBR"],
                        CAA_model_adj = tbl1sub_coverage_adj_sort[, "CAA_model"],
                        CAA_model_un = tbl1sub_coverage_un_sort[, "CAA_model"],
                        CAA_rerand_adj = tbl1sub_coverage_adj_sort[, "CAA_rerand"],
                        CAA_rerand_un = tbl1sub_coverage_un_sort[, "CAA_rerand"])

tbl1sub_bias <- cbind( tbl1sub_bias_adj_sort[,c(5:9)],
                        CR_adj = tbl1sub_bias_adj_sort[, "CR"],
                        CR_un = tbl1sub_bias_un_sort[, "CR"],
                        SBR_adj = tbl1sub_bias_adj_sort[, "SBR"],
                        SBR_un = tbl1sub_bias_un_sort[, "SBR"],
                        CAA_model_adj = tbl1sub_bias_adj_sort[, "CAA_model"],
                        CAA_model_un = tbl1sub_bias_un_sort[, "CAA_model"],
                        CAA_rerand_adj = tbl1sub_bias_adj_sort[, "CAA_rerand"],
                        CAA_rerand_un = tbl1sub_bias_un_sort[, "CAA_rerand"])

tbl1sub_power <- cbind( tbl1sub_power_adj_sort[,c(5:9)],
                        CR_adj = tbl1sub_power_adj_sort[, "CR"],
                        CR_un = tbl1sub_power_un_sort[, "CR"],
                        SBR_adj = tbl1sub_power_adj_sort[, "SBR"],
                        SBR_un = tbl1sub_power_un_sort[, "SBR"],
                        CAA_model_adj = tbl1sub_power_adj_sort[, "CAA_model"],
                        CAA_model_un = tbl1sub_power_un_sort[, "CAA_model"],
                        CAA_rerand_adj = tbl1sub_power_adj_sort[, "CAA_rerand"],
                        CAA_rerand_un = tbl1sub_power_un_sort[, "CAA_rerand"])
```


<!-- # Batch 2: Binary outcome (Y), continuous prognostic factors (X) {-} -->
```{r batch-2-binY-contX_coverage, cache = TRUE, echo = FALSE}
#' Adjusted analysis
tbl21_cov_adj <- subset( metrics_bycx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 1 ) )
tbl22_cov_adj <- subset( metrics_bycx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 1 ) )
tbl23_cov_adj <- subset( metrics_bycx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 1 ) )
tbl24_cov_adj <- subset( metrics_bycx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 1 ) )
#' Unadjusted analysis
tbl21_cov_un <- subset( metrics_bycx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 0 ) )
tbl22_cov_un <- subset( metrics_bycx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 0 ) )
tbl23_cov_un <- subset( metrics_bycx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 0 ) )
tbl24_cov_un <- subset( metrics_bycx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 0 ) )

#' Table 1a: Coverage (adjusted tx effect)
tbl2_coverage_adj <- cbind( CR = round( tbl21_cov_adj[,"coverage"], round_digits ),
                            SBR = round( tbl22_cov_adj[,"coverage"], round_digits ),
                            CAA_model = round( tbl23_cov_adj[,"coverage"], round_digits ),
                            CAA_rerand = rep(NA, times = nrow( tbl23_cov_adj )),  # TODO(michael): fix NA cell padding for missing values!

#                            CAA_rerand = round( tbl24_cov_adj[,"coverage"], round_digits ),
                            tbl23_cov_adj[,-1] )
dimnames( tbl2_coverage_adj )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )")

#' Table 1b: Coverage (adjusted tx effect)
tbl2_coverage_un <- cbind( CR = round( tbl21_cov_un[,"coverage"], round_digits ),
                            SBR = round( tbl22_cov_un[,"coverage"], round_digits ),
                            CAA_model = round( tbl23_cov_un[,"coverage"], round_digits ),
                           CAA_rerand = rep(NA, times = nrow( tbl23_cov_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                             CAA_rerand = round( tbl24_cov_un[,"coverage"], round_digits ),
                            tbl23_cov_un[,-1] )
dimnames( tbl2_coverage_un )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )")
```

```{r batch-2-binY-contX_bias, cache = TRUE, echo = FALSE}
#' Adjusted analysis
tbl21_bias_adj <- subset( metrics_bycx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 1 ) )
tbl22_bias_adj <- subset( metrics_bycx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 1 ) )
tbl23_bias_adj <- subset( metrics_bycx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 1 ) )
tbl24_bias_adj <- subset( metrics_bycx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 1 ) )
#' Unadjusted analysis
tbl21_bias_un <- subset( metrics_bycx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 0 ) )
tbl22_bias_un <- subset( metrics_bycx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 0 ) )
tbl23_bias_un <- subset( metrics_bycx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 0 ) )
tbl24_bias_un <- subset( metrics_bycx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 0 ) )

#' Table 1a: Coverage (adjusted tx effect)
tbl2_bias_adj <- cbind( CR = round( tbl21_bias_adj[,"bias"], round_digits ),
                            SBR = round( tbl22_bias_adj[,"bias"], round_digits ),
                            CAA_model = round( tbl23_bias_adj[,"bias"], round_digits ),
                        CAA_rerand = rep(NA, times = nrow( tbl23_bias_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                            CAA_rerand = round( tbl24_bias_adj[,"bias"], round_digits ),
                            tbl23_bias_adj[,-1] )
dimnames( tbl2_bias_adj )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )")

#' Table 1b: Coverage (adjusted tx effect)
tbl2_bias_un <- cbind( CR = round( tbl21_bias_un[,"bias"], round_digits ),
                            SBR = round( tbl22_bias_un[,"bias"], round_digits ),
                            CAA_model = round( tbl23_bias_un[,"bias"], round_digits ),
                           CAA_rerand = rep(NA, times = nrow( tbl23_bias_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                             CAA_rerand = round( tbl24_bias_un[,"bias"], round_digits ),
                            tbl23_bias_un[,-1] )
dimnames( tbl2_bias_un )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )")
```

```{r batch-2-binY-contX_power, cache = TRUE, echo = FALSE}
#' Adjusted analysis
tbl21_power_adj <- subset( metrics_bycx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 1 ) )
tbl22_power_adj <- subset( metrics_bycx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 1 ) )
tbl23_power_adj <- subset( metrics_bycx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 1 ) )
tbl24_power_adj <- subset( metrics_bycx, select = c( power.rerand, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 1 ) )
#' Unadjusted analysis
tbl21_power_un <- subset( metrics_bycx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 0 ) )
tbl22_power_un <- subset( metrics_bycx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 0 ) )
tbl23_power_un <- subset( metrics_bycx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 0 ) )
tbl24_power_un <- subset( metrics_bycx, select = c( power.rerand, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 0 ) )

#' Table 1a: Coverage (adjusted tx effect)
tbl2_power_adj <- cbind( CR = round( tbl21_power_adj[,"power.pvalue"], round_digits ),
                            SBR = round( tbl22_power_adj[,"power.pvalue"], round_digits ),
                            CAA_model = round( tbl23_power_adj[,"power.pvalue"], round_digits ),
                            CAA_rerand = rep(NA, times = nrow( tbl23_power_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                            CAA_rerand = round( tbl24_power_adj[,"power.rerand"], round_digits ),
                            tbl23_power_adj[,-1] )
dimnames( tbl2_power_adj )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )")

#' Table 1b: Coverage (adjusted tx effect)
tbl2_power_un <- cbind( CR = round( tbl21_power_un[,"power.pvalue"], round_digits ),
                            SBR = round( tbl22_power_un[,"power.pvalue"], round_digits ),
                            CAA_model = round( tbl23_power_un[,"power.pvalue"], round_digits ),
                           CAA_rerand = rep(NA, times = nrow( tbl23_power_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                             CAA_rerand = round( tbl24_power_un[,"power.rerand"], round_digits ),
                            tbl23_power_un[,-1] )
dimnames( tbl2_power_un )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )")
```

```{r batch-2-sort-subset, cache = TRUE, echo = FALSE}
# Ordering by $p(Y), p(X), \beta_Z, \beta_X$:
tbl2_coverage_adj_sort <- tbl2_coverage_adj[ do.call( order, tbl2_coverage_adj[,c(5, 8, 6, 7)] ), ]
tbl2_coverage_un_sort <- tbl2_coverage_un[ do.call( order, tbl2_coverage_un[,c(5, 8, 6, 7)] ), ]
tbl2_bias_adj_sort <- tbl2_bias_adj[ do.call( order, tbl2_bias_adj[,c(5, 8, 6, 7)] ), ]
tbl2_bias_un_sort <- tbl2_bias_un[ do.call( order, tbl2_bias_un[,c(5, 8, 6, 7)] ), ]
tbl2_power_adj_sort <- tbl2_power_adj[ do.call( order, tbl2_power_adj[,c(5, 8, 6, 7)] ), ]
tbl2_power_un_sort <- tbl2_power_un[ do.call( order, tbl2_power_un[,c(5, 8, 6, 7)] ), ]
```

```{r batch-2-adj-unadj-tables, cache = TRUE, echo = FALSE}
tbl2_coverage <- cbind( tbl2_coverage_adj_sort[,c(5:8)],
                        CR_adj = tbl2_coverage_adj_sort[, "CR"],
                        CR_un = tbl2_coverage_un_sort[, "CR"],
                        SBR_adj = tbl2_coverage_adj_sort[, "SBR"],
                        SBR_un = tbl2_coverage_un_sort[, "SBR"],
                        CAA_model_adj = tbl2_coverage_adj_sort[, "CAA_model"],
                        CAA_model_un = tbl2_coverage_un_sort[, "CAA_model"],
                        CAA_rerand_adj = tbl2_coverage_adj_sort[, "CAA_rerand"],
                        CAA_rerand_un = tbl2_coverage_un_sort[, "CAA_rerand"])

tbl2_bias <- cbind( tbl2_bias_adj_sort[,c(5:8)],
                        CR_adj = tbl2_bias_adj_sort[, "CR"],
                        CR_un = tbl2_bias_un_sort[, "CR"],
                        SBR_adj = tbl2_bias_adj_sort[, "SBR"],
                        SBR_un = tbl2_bias_un_sort[, "SBR"],
                        CAA_model_adj = tbl2_bias_adj_sort[, "CAA_model"],
                        CAA_model_un = tbl2_bias_un_sort[, "CAA_model"],
                        CAA_rerand_adj = tbl2_bias_adj_sort[, "CAA_rerand"],
                        CAA_rerand_un = tbl2_bias_un_sort[, "CAA_rerand"])

tbl2_power <- cbind( tbl2_power_adj_sort[,c(5:8)],
                        CR_adj = tbl2_power_adj_sort[, "CR"],
                        CR_un = tbl2_power_un_sort[, "CR"],
                        SBR_adj = tbl2_power_adj_sort[, "SBR"],
                        SBR_un = tbl2_power_un_sort[, "SBR"],
                        CAA_model_adj = tbl2_power_adj_sort[, "CAA_model"],
                        CAA_model_un = tbl2_power_un_sort[, "CAA_model"],
                        CAA_rerand_adj = tbl2_power_adj_sort[, "CAA_rerand"],
                        CAA_rerand_un = tbl2_power_un_sort[, "CAA_rerand"])
```

<!-- BATCH 2 of 4, SUBSETTING ON VALID simulations -->
```{r batch-2-subset-binY-contX_coverage, cache = TRUE, echo = FALSE}
#' Adjusted analysis
tbl2sub1_cov_adj <- subset( metrics_bycx_sub, select = c( nsim, coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 1 ) )
tbl2sub2_cov_adj <- subset( metrics_bycx_sub, select = c( nsim, coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 1 ) )
tbl2sub3_cov_adj <- subset( metrics_bycx_sub, select = c( nsim, coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 1 ) )
tbl2sub4_cov_adj <- subset( metrics_bycx_sub, select = c( nsim, coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 1 ) )
#' Unadjusted analysis
tbl2sub1_cov_un <- subset( metrics_bycx_sub, select = c( nsim, coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 0 ) )
tbl2sub2_cov_un <- subset( metrics_bycx_sub, select = c( nsim, coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 0 ) )
tbl2sub3_cov_un <- subset( metrics_bycx_sub, select = c( nsim, coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 0 ) )
tbl2sub4_cov_un <- subset( metrics_bycx_sub, select = c( nsim, coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 0 ) )

#' Table 1a: Coverage (adjusted tx effect)
tbl2sub_coverage_adj <- cbind( CR = round( tbl2sub1_cov_adj[,"coverage"], round_digits ),
                            SBR = round( tbl2sub2_cov_adj[,"coverage"], round_digits ),
                            CAA_model = round( tbl2sub3_cov_adj[,"coverage"], round_digits ),
                            CAA_rerand = rep(NA, times = nrow( tbl2sub3_cov_adj )),  # TODO(michael): fix NA cell padding for missing values!

#                            CAA_rerand = round( tbl2sub4_cov_adj[,"coverage"], round_digits ),
                            tbl2sub3_cov_adj[,-1] )
dimnames( tbl2sub_coverage_adj )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )")

#' Table 1b: Coverage (adjusted tx effect)
tbl2sub_coverage_un <- cbind( CR = round( tbl2sub1_cov_un[,"coverage"], round_digits ),
                            SBR = round( tbl2sub2_cov_un[,"coverage"], round_digits ),
                            CAA_model = round( tbl2sub3_cov_un[,"coverage"], round_digits ),
                           CAA_rerand = rep(NA, times = nrow( tbl2sub3_cov_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                             CAA_rerand = round( tbl2sub4_cov_un[,"coverage"], round_digits ),
                            tbl2sub3_cov_un[,-1] )
dimnames( tbl2sub_coverage_un )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )")
```

```{r batch-2-subset-binY-contX_bias, cache = TRUE, echo = FALSE}
#' Adjusted analysis
tbl2sub1_bias_adj <- subset( metrics_bycx_sub, select = c( nsim, bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 1 ) )
tbl2sub2_bias_adj <- subset( metrics_bycx_sub, select = c( nsim, bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 1 ) )
tbl2sub3_bias_adj <- subset( metrics_bycx_sub, select = c( nsim, bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 1 ) )
tbl2sub4_bias_adj <- subset( metrics_bycx_sub, select = c( nsim, bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 1 ) )
#' Unadjusted analysis
tbl2sub1_bias_un <- subset( metrics_bycx_sub, select = c( nsim, bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 0 ) )
tbl2sub2_bias_un <- subset( metrics_bycx_sub, select = c( nsim, bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 0 ) )
tbl2sub3_bias_un <- subset( metrics_bycx_sub, select = c( nsim, bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 0 ) )
tbl2sub4_bias_un <- subset( metrics_bycx_sub, select = c( nsim, bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 0 ) )

#' Table 1a: Coverage (adjusted tx effect)
tbl2sub_bias_adj <- cbind( CR = round( tbl2sub1_bias_adj[,"bias"], round_digits ),
                            SBR = round( tbl2sub2_bias_adj[,"bias"], round_digits ),
                            CAA_model = round( tbl2sub3_bias_adj[,"bias"], round_digits ),
                        CAA_rerand = rep(NA, times = nrow( tbl2sub3_bias_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                            CAA_rerand = round( tbl2sub4_bias_adj[,"bias"], round_digits ),
                            tbl2sub3_bias_adj[,-1] )
dimnames( tbl2sub_bias_adj )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )")

#' Table 1b: Coverage (adjusted tx effect)
tbl2sub_bias_un <- cbind( CR = round( tbl2sub1_bias_un[,"bias"], round_digits ),
                            SBR = round( tbl2sub2_bias_un[,"bias"], round_digits ),
                            CAA_model = round( tbl2sub3_bias_un[,"bias"], round_digits ),
                           CAA_rerand = rep(NA, times = nrow( tbl2sub3_bias_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                             CAA_rerand = round( tbl2sub4_bias_un[,"bias"], round_digits ),
                            tbl2sub3_bias_un[,-1] )
dimnames( tbl2sub_bias_un )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )")
```

```{r batch-2-subset-binY-contX_power, cache = TRUE, echo = FALSE}
#' Adjusted analysis
tbl2sub1_power_adj <- subset( metrics_bycx_sub, select = c( nsim, power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 1 ) )
tbl2sub2_power_adj <- subset( metrics_bycx_sub, select = c( nsim, power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 1 ) )
tbl2sub3_power_adj <- subset( metrics_bycx_sub, select = c( nsim, power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 1 ) )
tbl2sub4_power_adj <- subset( metrics_bycx_sub, select = c( nsim, power.rerand, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 1 ) )
#' Unadjusted analysis
tbl2sub1_power_un <- subset( metrics_bycx_sub, select = c( nsim, power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 0 ) )
tbl2sub2_power_un <- subset( metrics_bycx_sub, select = c( nsim, power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 0 ) )
tbl2sub3_power_un <- subset( metrics_bycx_sub, select = c( nsim, power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 0 ) )
tbl2sub4_power_un <- subset( metrics_bycx_sub, select = c( nsim, power.rerand, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, outcome_marginal_prevalence),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 0 ) )

#' Table 1a: Coverage (adjusted tx effect)
tbl2sub_power_adj <- cbind( CR = round( tbl2sub1_power_adj[,"power.pvalue"], round_digits ),
                            SBR = round( tbl2sub2_power_adj[,"power.pvalue"], round_digits ),
                            CAA_model = round( tbl2sub3_power_adj[,"power.pvalue"], round_digits ),
                            CAA_rerand = rep(NA, times = nrow( tbl2sub3_power_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                            CAA_rerand = round( tbl2sub4_power_adj[,"power.rerand"], round_digits ),
                            tbl2sub3_power_adj[,-1] )
dimnames( tbl2sub_power_adj )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )")

#' Table 1b: Coverage (adjusted tx effect)
tbl2sub_power_un <- cbind( CR = round( tbl2sub1_power_un[,"power.pvalue"], round_digits ),
                            SBR = round( tbl2sub2_power_un[,"power.pvalue"], round_digits ),
                            CAA_model = round( tbl2sub3_power_un[,"power.pvalue"], round_digits ),
                           CAA_rerand = rep(NA, times = nrow( tbl2sub3_power_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                             CAA_rerand = round( tbl2sub4_power_un[,"power.rerand"], round_digits ),
                            tbl2sub3_power_un[,-1] )
dimnames( tbl2sub_power_un )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )")
```

```{r batch-2-subset-sort-subset, cache = TRUE, echo = FALSE}
# Ordering by $p(Y), p(X), \beta_Z, \beta_X$:
tbl2sub_coverage_adj_sort <- tbl2sub_coverage_adj[ do.call( order, tbl2sub_coverage_adj[,c(5, 8, 6, 7)] ), ]
tbl2sub_coverage_un_sort <- tbl2sub_coverage_un[ do.call( order, tbl2sub_coverage_un[,c(5, 8, 6, 7)] ), ]
tbl2sub_bias_adj_sort <- tbl2sub_bias_adj[ do.call( order, tbl2sub_bias_adj[,c(5, 8, 6, 7)] ), ]
tbl2sub_bias_un_sort <- tbl2sub_bias_un[ do.call( order, tbl2sub_bias_un[,c(5, 8, 6, 7)] ), ]
tbl2sub_power_adj_sort <- tbl2sub_power_adj[ do.call( order, tbl2sub_power_adj[,c(5, 8, 6, 7)] ), ]
tbl2sub_power_un_sort <- tbl2sub_power_un[ do.call( order, tbl2sub_power_un[,c(5, 8, 6, 7)] ), ]
```

```{r batch-2-subset-adj-unadj-tables, cache = TRUE, echo = FALSE}
tbl2sub_coverage <- cbind( tbl2sub_coverage_adj_sort[,c(5:8)],
                        CR_adj = tbl2sub_coverage_adj_sort[, "CR"],
                        CR_un = tbl2sub_coverage_un_sort[, "CR"],
                        SBR_adj = tbl2sub_coverage_adj_sort[, "SBR"],
                        SBR_un = tbl2sub_coverage_un_sort[, "SBR"],
                        CAA_model_adj = tbl2sub_coverage_adj_sort[, "CAA_model"],
                        CAA_model_un = tbl2sub_coverage_un_sort[, "CAA_model"],
                        CAA_rerand_adj = tbl2sub_coverage_adj_sort[, "CAA_rerand"],
                        CAA_rerand_un = tbl2sub_coverage_un_sort[, "CAA_rerand"])

tbl2sub_bias <- cbind( tbl2sub_bias_adj_sort[,c(5:8)],
                        CR_adj = tbl2sub_bias_adj_sort[, "CR"],
                        CR_un = tbl2sub_bias_un_sort[, "CR"],
                        SBR_adj = tbl2sub_bias_adj_sort[, "SBR"],
                        SBR_un = tbl2sub_bias_un_sort[, "SBR"],
                        CAA_model_adj = tbl2sub_bias_adj_sort[, "CAA_model"],
                        CAA_model_un = tbl2sub_bias_un_sort[, "CAA_model"],
                        CAA_rerand_adj = tbl2sub_bias_adj_sort[, "CAA_rerand"],
                        CAA_rerand_un = tbl2sub_bias_un_sort[, "CAA_rerand"])

tbl2sub_power <- cbind( tbl2sub_power_adj_sort[,c(5:8)],
                        CR_adj = tbl2sub_power_adj_sort[, "CR"],
                        CR_un = tbl2sub_power_un_sort[, "CR"],
                        SBR_adj = tbl2sub_power_adj_sort[, "SBR"],
                        SBR_un = tbl2sub_power_un_sort[, "SBR"],
                        CAA_model_adj = tbl2sub_power_adj_sort[, "CAA_model"],
                        CAA_model_un = tbl2sub_power_un_sort[, "CAA_model"],
                        CAA_rerand_adj = tbl2sub_power_adj_sort[, "CAA_rerand"],
                        CAA_rerand_un = tbl2sub_power_un_sort[, "CAA_rerand"])
```

<!-- # Batch 3: Continuous outcome (Y), binary prognostic factors (X) {-} -->
```{r batch-3-contY-binX_coverage, cache = TRUE, echo = FALSE}
#' Adjusted analysis
tbl31_cov_adj <- subset( metrics_cybx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 1 ) )
tbl32_cov_adj <- subset( metrics_cybx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 1 ) )
tbl33_cov_adj <- subset( metrics_cybx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 1 ) )
tbl34_cov_adj <- subset( metrics_cybx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 1 ) )
#' Unadjusted analysis
tbl31_cov_un <- subset( metrics_cybx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 0 ) )
tbl32_cov_un <- subset( metrics_cybx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 0 ) )
tbl33_cov_un <- subset( metrics_cybx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 0 ) )
tbl34_cov_un <- subset( metrics_cybx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 0 ) )

#' Table 1a: Coverage (adjusted tx effect)
tbl3_coverage_adj <- cbind( CR = round( tbl31_cov_adj[,"coverage"], round_digits ),
                            SBR = round( tbl32_cov_adj[,"coverage"], round_digits ),
                            CAA_model = round( tbl33_cov_adj[,"coverage"], round_digits ),
                            CAA_rerand = round( tbl34_cov_adj[,"coverage"], round_digits ),
                            tbl33_cov_adj[,-1] )
dimnames( tbl3_coverage_adj )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( X )")

#' Table 1b: Coverage (adjusted tx effect)
tbl3_coverage_un <- cbind( CR = round( tbl31_cov_un[,"coverage"], round_digits ),
                            SBR = round( tbl32_cov_un[,"coverage"], round_digits ),
                            CAA_model = round( tbl33_cov_un[,"coverage"], round_digits ),
#                           CAA_rerand = rep(NA, times = nrow( tbl34_cov_adj )),  # TODO(michael): fix NA cell padding for missing values!
                            CAA_rerand = round( tbl34_cov_un[,"coverage"], round_digits ),
                            tbl33_cov_un[,-1] )
dimnames( tbl3_coverage_un )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( X )")
```

```{r batch-3-contY-binX_bias, cache = TRUE, echo = FALSE}
#' Adjusted analysis
tbl31_bias_adj <- subset( metrics_cybx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 1 ) )
tbl32_bias_adj <- subset( metrics_cybx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 1 ) )
tbl33_bias_adj <- subset( metrics_cybx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 1 ) )
tbl34_bias_adj <- subset( metrics_cybx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 1 ) )
#' Unadjusted analysis
tbl31_bias_un <- subset( metrics_cybx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 0 ) )
tbl32_bias_un <- subset( metrics_cybx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 0 ) )
tbl33_bias_un <- subset( metrics_cybx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 0 ) )
tbl34_bias_un <- subset( metrics_cybx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 0 ) )

#' Table 1a: Coverage (adjusted tx effect)
tbl3_bias_adj <- cbind( CR = round( tbl31_bias_adj[,"bias"], round_digits ),
                            SBR = round( tbl32_bias_adj[,"bias"], round_digits ),
                            CAA_model = round( tbl33_bias_adj[,"bias"], round_digits ),
                            CAA_rerand = round( tbl34_bias_adj[,"bias"], round_digits ),
                            tbl33_bias_adj[,-1] )
dimnames( tbl3_bias_adj )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( X )")

#' Table 1b: Coverage (adjusted tx effect)
tbl3_bias_un <- cbind( CR = round( tbl31_bias_un[,"bias"], round_digits ),
                            SBR = round( tbl32_bias_un[,"bias"], round_digits ),
                            CAA_model = round( tbl33_bias_un[,"bias"], round_digits ),
                           CAA_rerand = rep(NA, times = nrow( tbl34_bias_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                             CAA_rerand = round( tbl34_bias_un[,"bias"], round_digits ),
                            tbl33_bias_un[,-1] )
dimnames( tbl3_bias_un )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( X )")
```

```{r batch-3-contY-binX_power, cache = TRUE, echo = FALSE}
#' Adjusted analysis
tbl31_power_adj <- subset( metrics_cybx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 1 ) )
tbl32_power_adj <- subset( metrics_cybx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 1 ) )
tbl33_power_adj <- subset( metrics_cybx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 1 ) )
tbl34_power_adj <- subset( metrics_cybx, select = c( power.rerand, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 1 ) )
#' Unadjusted analysis
tbl31_power_un <- subset( metrics_cybx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 0 ) )
tbl32_power_un <- subset( metrics_cybx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 0 ) )
tbl33_power_un <- subset( metrics_cybx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 0 ) )
tbl34_power_un <- subset( metrics_cybx, select = c( power.rerand, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size, prognostic_factor_prevalence ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 0 ) )

#' Table 1a: Coverage (adjusted tx effect)
tbl3_power_adj <- cbind( CR = round( tbl31_power_adj[,"power.pvalue"], round_digits ),
                            SBR = round( tbl32_power_adj[,"power.pvalue"], round_digits ),
                            CAA_model = round( tbl33_power_adj[,"power.pvalue"], round_digits ),
                            CAA_rerand = round( tbl34_power_adj[,"power.rerand"], round_digits ),
                            tbl33_power_adj[,-1] )
dimnames( tbl3_power_adj )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( X )")

#' Table 1b: Coverage (adjusted tx effect)
tbl3_power_un <- cbind( CR = round( tbl31_power_un[,"power.pvalue"], round_digits ),
                            SBR = round( tbl32_power_un[,"power.pvalue"], round_digits ),
                            CAA_model = round( tbl33_power_un[,"power.pvalue"], round_digits ),
                           CAA_rerand = rep(NA, times = nrow( tbl34_power_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                             CAA_rerand = round( tbl34_power_un[,"power.rerand"], round_digits ),
                            tbl33_power_un[,-1] )
dimnames( tbl3_power_un )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( X )")
```

```{r batch-3-sort-subset, cache = TRUE, echo = FALSE}
# Ordering by $p(Y), p(X), \beta_Z, \beta_X$:
tbl3_coverage_adj_sort <- tbl3_coverage_adj[ do.call( order, tbl3_coverage_adj[,c(5, 8, 6, 7)] ), ]
tbl3_coverage_un_sort <- tbl3_coverage_un[ do.call( order, tbl3_coverage_un[,c(5, 8, 6, 7)] ), ]
tbl3_bias_adj_sort <- tbl3_bias_adj[ do.call( order, tbl3_bias_adj[,c(5, 8, 6, 7)] ), ]
tbl3_bias_un_sort <- tbl3_bias_un[ do.call( order, tbl3_bias_un[,c(5, 8, 6, 7)] ), ]
tbl3_power_adj_sort <- tbl3_power_adj[ do.call( order, tbl3_power_adj[,c(5, 8, 6, 7)] ), ]
tbl3_power_un_sort <- tbl3_power_un[ do.call( order, tbl3_power_un[,c(5, 8, 6, 7)] ), ]
```

```{r batch-3-adj-unadj-tables, cache = TRUE, echo = FALSE}
tbl3_coverage <- cbind( tbl3_coverage_adj_sort[,c(5:8)],
                        CR_adj = tbl3_coverage_adj_sort[, "CR"],
                        CR_un = tbl3_coverage_un_sort[, "CR"],
                        SBR_adj = tbl3_coverage_adj_sort[, "SBR"],
                        SBR_un = tbl3_coverage_un_sort[, "SBR"],
                        CAA_model_adj = tbl3_coverage_adj_sort[, "CAA_model"],
                        CAA_model_un = tbl3_coverage_un_sort[, "CAA_model"],
                        CAA_rerand_adj = tbl3_coverage_adj_sort[, "CAA_rerand"],
                        CAA_rerand_un = tbl3_coverage_un_sort[, "CAA_rerand"])

tbl3_bias <- cbind( tbl3_bias_adj_sort[,c(5:8)],
                        CR_adj = tbl3_bias_adj_sort[, "CR"],
                        CR_un = tbl3_bias_un_sort[, "CR"],
                        SBR_adj = tbl3_bias_adj_sort[, "SBR"],
                        SBR_un = tbl3_bias_un_sort[, "SBR"],
                        CAA_model_adj = tbl3_bias_adj_sort[, "CAA_model"],
                        CAA_model_un = tbl3_bias_un_sort[, "CAA_model"],
                        CAA_rerand_adj = tbl3_bias_adj_sort[, "CAA_rerand"],
                        CAA_rerand_un = tbl3_bias_un_sort[, "CAA_rerand"])

tbl3_power <- cbind( tbl3_power_adj_sort[,c(5:8)],
                        CR_adj = tbl3_power_adj_sort[, "CR"],
                        CR_un = tbl3_power_un_sort[, "CR"],
                        SBR_adj = tbl3_power_adj_sort[, "SBR"],
                        SBR_un = tbl3_power_un_sort[, "SBR"],
                        CAA_model_adj = tbl3_power_adj_sort[, "CAA_model"],
                        CAA_model_un = tbl3_power_un_sort[, "CAA_model"],
                        CAA_rerand_adj = tbl3_power_adj_sort[, "CAA_rerand"],
                        CAA_rerand_un = tbl3_power_un_sort[, "CAA_rerand"])
```

<!-- # Batch 4: Continuous outcome (Y), continuous prognostic factors (X) {-} -->
```{r batch-4-binY-binX_coverage, cache = TRUE, echo = FALSE}
#' Adjusted analysis
tbl41_cov_adj <- subset( metrics_cycx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 1 ) )
tbl42_cov_adj <- subset( metrics_cycx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 1 ) )
tbl43_cov_adj <- subset( metrics_cycx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 1 ) )
tbl44_cov_adj <- subset( metrics_cycx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 1 ) )
#' Unadjusted analysis
tbl41_cov_un <- subset( metrics_cycx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 0 ) )
tbl42_cov_un <- subset( metrics_cycx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 0 ) )
tbl43_cov_un <- subset( metrics_cycx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 0 ) )
tbl44_cov_un <- subset( metrics_cycx, select = c( coverage, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 0 ) )

#' Table 1a: Coverage (adjusted tx effect)
tbl4_coverage_adj <- cbind( CR = round( tbl41_cov_adj[,"coverage"], round_digits ),
                            SBR = round( tbl42_cov_adj[,"coverage"], round_digits ),
                            CAA_model = round( tbl43_cov_adj[,"coverage"], round_digits ),
                            CAA_rerand = round( tbl44_cov_adj[,"coverage"], round_digits ),
                            tbl43_cov_adj[,-1] )
dimnames( tbl4_coverage_adj )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX")

#' Table 1b: Coverage (adjusted tx effect)
tbl4_coverage_un <- cbind( CR = round( tbl41_cov_un[,"coverage"], round_digits ),
                            SBR = round( tbl42_cov_un[,"coverage"], round_digits ),
                            CAA_model = round( tbl43_cov_un[,"coverage"], round_digits ),
                           CAA_rerand = rep(NA, times = nrow( tbl44_cov_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                             CAA_rerand = round( tbl44_cov_un[,"coverage"], round_digits ),
                            tbl43_cov_un[,-1] )
dimnames( tbl4_coverage_un )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX")
```

```{r batch-4-binY-binX_bias, cache = TRUE, echo = FALSE}
#' Adjusted analysis
tbl41_bias_adj <- subset( metrics_cycx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 1 ) )
tbl42_bias_adj <- subset( metrics_cycx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 1 ) )
tbl43_bias_adj <- subset( metrics_cycx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 1 ) )
tbl44_bias_adj <- subset( metrics_cycx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 1 ) )
#' Unadjusted analysis
tbl41_bias_un <- subset( metrics_cycx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 0 ) )
tbl42_bias_un <- subset( metrics_cycx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 0 ) )
tbl43_bias_un <- subset( metrics_cycx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 0 ) )
tbl44_bias_un <- subset( metrics_cycx, select = c( bias, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 0 ) )

#' Table 1a: Coverage (adjusted tx effect)
tbl4_bias_adj <- cbind( CR = round( tbl41_bias_adj[,"bias"], round_digits ),
                            SBR = round( tbl42_bias_adj[,"bias"], round_digits ),
                            CAA_model = round( tbl43_bias_adj[,"bias"], round_digits ),
                            CAA_rerand = round( tbl44_bias_adj[,"bias"], round_digits ),
                            tbl43_bias_adj[,-1] )
dimnames( tbl4_bias_adj )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX")

#' Table 1b: Coverage (adjusted tx effect)
tbl4_bias_un <- cbind( CR = round( tbl41_bias_un[,"bias"], round_digits ),
                            SBR = round( tbl42_bias_un[,"bias"], round_digits ),
                            CAA_model = round( tbl43_bias_un[,"bias"], round_digits ),
                           CAA_rerand = rep(NA, times = nrow( tbl44_bias_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                             CAA_rerand = round( tbl44_bias_un[,"bias"], round_digits ),
                            tbl43_bias_un[,-1] )
dimnames( tbl4_bias_un )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX")
```

```{r batch-4-binY-binX_power, cache = TRUE, echo = FALSE}
#' Adjusted analysis
tbl41_power_adj <- subset( metrics_cycx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 1 ) )
tbl42_power_adj <- subset( metrics_cycx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 1 ) )
tbl43_power_adj <- subset( metrics_cycx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 1 ) )
tbl44_power_adj <- subset( metrics_cycx, select = c( power.rerand, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 1 ) )
#' Unadjusted analysis
tbl41_power_un <- subset( metrics_cycx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "CR" & rerandomized == 0 & adjusted == 0 ) )
tbl42_power_un <- subset( metrics_cycx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "SBR" & rerandomized == 0 & adjusted == 0 ) )
tbl43_power_un <- subset( metrics_cycx, select = c( power.pvalue, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == 0 ) )
tbl44_power_un <- subset( metrics_cycx, select = c( power.rerand, trial_size, treatment_assignment_effect_size, prognostic_factor_effect_size ),
                          subset = ( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == 0 ) )

#' Table 1a: Coverage (adjusted tx effect)
tbl4_power_adj <- cbind( CR = round( tbl41_power_adj[,"power.pvalue"], round_digits ),
                            SBR = round( tbl42_power_adj[,"power.pvalue"], round_digits ),
                            CAA_model = round( tbl43_power_adj[,"power.pvalue"], round_digits ),
                            CAA_rerand = round( tbl44_power_adj[,"power.rerand"], round_digits ),
                            tbl43_power_adj[,-1] )
dimnames( tbl4_power_adj )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX")

#' Table 1b: Coverage (adjusted tx effect)
tbl4_power_un <- cbind( CR = round( tbl41_power_un[,"power.pvalue"], round_digits ),
                            SBR = round( tbl42_power_un[,"power.pvalue"], round_digits ),
                            CAA_model = round( tbl43_power_un[,"power.pvalue"], round_digits ),
                           CAA_rerand = rep(NA, times = nrow( tbl44_power_adj )),  # TODO(michael): fix NA cell padding for missing values!
#                             CAA_rerand = round( tbl44_power_un[,"power.rerand"], round_digits ),
                            tbl43_power_un[,-1] )
dimnames( tbl4_power_un )[[2]] <- c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX")
```

```{r batch-4-sort-subset, cache = TRUE, echo = FALSE}
# Ordering by $p(Y), p(X), \beta_Z, \beta_X$:
tbl4_coverage_adj_sort <- tbl4_coverage_adj[ do.call( order, tbl4_coverage_adj[,c(5, 6, 7)] ), ]
tbl4_coverage_un_sort <- tbl4_coverage_un[ do.call( order, tbl4_coverage_un[,c(5, 6, 7)] ), ]
tbl4_bias_adj_sort <- tbl4_bias_adj[ do.call( order, tbl4_bias_adj[,c(5, 6, 7)] ), ]
tbl4_bias_un_sort <- tbl4_bias_un[ do.call( order, tbl4_bias_un[,c(5, 6, 7)] ), ]
tbl4_power_adj_sort <- tbl4_power_adj[ do.call( order, tbl4_power_adj[,c(5, 6, 7)] ), ]
tbl4_power_un_sort <- tbl4_power_un[ do.call( order, tbl4_power_un[,c(5, 6, 7)] ), ]
```

```{r batch-4-adj-unadj-tables, cache = TRUE, echo = FALSE}
tbl4_coverage <- cbind( tbl4_coverage_adj_sort[,c(5:7)],
                        CR_adj = tbl4_coverage_adj_sort[, "CR"],
                        CR_un = tbl4_coverage_un_sort[, "CR"],
                        SBR_adj = tbl4_coverage_adj_sort[, "SBR"],
                        SBR_un = tbl4_coverage_un_sort[, "SBR"],
                        CAA_model_adj = tbl4_coverage_adj_sort[, "CAA_model"],
                        CAA_model_un = tbl4_coverage_un_sort[, "CAA_model"],
                        CAA_rerand_adj = tbl4_coverage_adj_sort[, "CAA_rerand"],
                        CAA_rerand_un = tbl4_coverage_un_sort[, "CAA_rerand"])

tbl4_bias <- cbind( tbl4_bias_adj_sort[,c(5:7)],
                        CR_adj = tbl4_bias_adj_sort[, "CR"],
                        CR_un = tbl4_bias_un_sort[, "CR"],
                        SBR_adj = tbl4_bias_adj_sort[, "SBR"],
                        SBR_un = tbl4_bias_un_sort[, "SBR"],
                        CAA_model_adj = tbl4_bias_adj_sort[, "CAA_model"],
                        CAA_model_un = tbl4_bias_un_sort[, "CAA_model"],
                        CAA_rerand_adj = tbl4_bias_adj_sort[, "CAA_rerand"],
                        CAA_rerand_un = tbl4_bias_un_sort[, "CAA_rerand"])

tbl4_power <- cbind( tbl4_power_adj_sort[,c(5:7)],
                        CR_adj = tbl4_power_adj_sort[, "CR"],
                        CR_un = tbl4_power_un_sort[, "CR"],
                        SBR_adj = tbl4_power_adj_sort[, "SBR"],
                        SBR_un = tbl4_power_un_sort[, "SBR"],
                        CAA_model_adj = tbl4_power_adj_sort[, "CAA_model"],
                        CAA_model_un = tbl4_power_un_sort[, "CAA_model"],
                        CAA_rerand_adj = tbl4_power_adj_sort[, "CAA_rerand"],
                        CAA_rerand_un = tbl4_power_un_sort[, "CAA_rerand"])
```


<!-- Printed tables are below:  -->

# Results {-}

## Batch 1: Binary outcome (Y), binary prognostic factors (X) {-}
### Complete simulation results (5010 simulations)
```{r batch-1-table-settings, cache = TRUE, echo = FALSE, results = 'asis'}
.col.names.b1 = c("n", "bZ", "bX", "Pr( Y )", "Pr( X )", "adj", "unadj", "adj", "unadj", "adj", "unadj", "adj");
.align.b1 = c(rep("c", 5), rep("r", 6), "c");
.latex_options.b1 = c("striped", "bordered", "hold_position")
.header.randomization.method.b1 = c(" " = 5, "CR" = 2, "SBR" = 2, "CAA" = 2, "CAA" = 1);
.header.analysis.method.b1 = c(" " = 5, "Model-based" = 6, "Rerandomization" = 1);
.batch.labels <- paste0("Table ", 1, c("a", "b", "c", "d", "e", "f"), 
                        ": (Binary Y, binary X) ",
                        c("Coverage probability", "Bias", "Power"))
.linesep = kable_booktabs_linesep( nlines = 6 )
```

```{r batch-1-coverage-table, cache = TRUE, echo = FALSE, results='asis'}
tbl1_coverage[, -dim( tbl1_coverage )[2]] %>%
kable( caption = .batch.labels[ 1 ], row.names = FALSE, 
       col.names = .col.names.b1, align = .align.b1, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b1, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b1 ) %>%
  add_header_above( .header.analysis.method.b1 )
```

\newpage
```{r batch-1-bias-table, cache = TRUE, echo = FALSE, results='asis'}
tbl1_bias[, -dim( tbl1_bias )[2]] %>%
kable( caption = .batch.labels[ 2 ], row.names = FALSE, 
       col.names = .col.names.b1, align = .align.b1, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b1, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b1 ) %>%
  add_header_above( .header.analysis.method.b1 )
```

\newpage
```{r batch-1-power-table, cache = TRUE, echo = FALSE, results='asis'}
tbl1_power[, -dim( tbl1_bias )[2]] %>%
kable( caption = .batch.labels[ 3 ], row.names = FALSE, 
       col.names = .col.names.b1, align = .align.b1, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b1, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b1 ) %>%
  add_header_above( .header.analysis.method.b1 )
```

\newpage
### Subsetted simulation results (simulations without non-complete separation)
```{r batch-1-subset-coverage-table, cache = TRUE, echo = FALSE, results='asis'}
tbl1sub_coverage[, -dim( tbl1sub_coverage )[2]] %>%
kable( caption = .batch.labels[ 4 ], row.names = FALSE, 
       col.names = .col.names.b1, align = .align.b1, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b1, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b1 ) %>%
  add_header_above( .header.analysis.method.b1 )
```

\newpage
```{r batch-1-subset-bias-table, cache = TRUE, echo = FALSE, results='asis'}
tbl1sub_bias[, -dim( tbl1sub_bias )[2]] %>%
kable( caption = .batch.labels[ 5 ], row.names = FALSE, 
       col.names = .col.names.b1, align = .align.b1, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b1, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b1 ) %>%
  add_header_above( .header.analysis.method.b1 )
```

\newpage
```{r batch-1-subset-power-table, cache = TRUE, echo = FALSE, results='asis'}
tbl1sub_power[, -dim( tbl1sub_power )[2]] %>%
kable( caption = .batch.labels[ 6 ], row.names = FALSE, 
       col.names = .col.names.b1, align = .align.b1, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b1, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b1 ) %>%
  add_header_above( .header.analysis.method.b1 )
```


\newpage
## Batch 2: Binary outcome (Y), continuous prognostic factors (X) {-}
```{r batch-2-table-settings, cache = TRUE, echo = FALSE, results = 'asis'}
.col.names.b2 = c("n", "exp( bZ )", "exp( bX )", "Pr( Y )", "adj", "unadj", "adj", "unadj", "adj", "unadj", "adj");
.align.b2 = c(rep("c", 4), rep("r", 6), "c");
.latex_options.b2 = c("striped", "bordered", "hold_position")
.header.randomization.method.b2 = c(" " = 4, "CR" = 2, "SBR" = 2, "CAA" = 2, "CAA" = 1);
.header.analysis.method.b2 = c(" " = 4, "Model-based" = 6, "Rerandomization" = 1);

.batch.labels <- paste0("Table ", 2, c("a", "b", "c", "d", "e", "f"), 
                        ": (Binary Y, continuous X) ",
                        c("Coverage probability", "Bias", "Power"))

.linesep = kable_booktabs_linesep( nlines = 6 )
```

### Complete simulation results (5010 simulations)
```{r batch-2-coverage-table, cache = TRUE, echo = FALSE, results='asis'}
tbl2_coverage[, -dim( tbl2_coverage )[2]] %>%
kable( caption = .batch.labels[ 1 ], row.names = FALSE, 
       col.names = .col.names.b2, align = .align.b2, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b2, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b2 ) %>%
  add_header_above( .header.analysis.method.b2 )
```

\newpage
```{r batch-2-bias-table, cache = TRUE, echo = FALSE, results='asis'}
tbl2_bias[, -dim( tbl2_bias )[2]] %>%
kable( caption = .batch.labels[ 2 ], row.names = FALSE, 
       col.names = .col.names.b2, align = .align.b2, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b2, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b2 ) %>%
  add_header_above( .header.analysis.method.b2 )
```

\newpage
```{r batch-2-power-table, cache = TRUE, echo = FALSE, results='asis'}
tbl2_power[, -dim( tbl2_power )[2]] %>%
kable( caption = .batch.labels[ 3 ], row.names = FALSE, 
       col.names = .col.names.b2, align = .align.b2, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b2, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b2 ) %>%
  add_header_above( .header.analysis.method.b2 )
```

\newpage
### Subsetted simulation results (simulations without non-complete separation)
```{r batch-2-subset-coverage-table, cache = TRUE, echo = FALSE, results='asis'}
tbl2sub_coverage[, -dim( tbl2sub_coverage )[2]] %>%
kable( caption = .batch.labels[ 4 ], row.names = FALSE, 
       col.names = .col.names.b2, align = .align.b2, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b2, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b2 ) %>%
  add_header_above( .header.analysis.method.b2 )
```

\newpage
```{r batch-2-subset-bias-table, cache = TRUE, echo = FALSE, results='asis'}
tbl2sub_bias[, -dim( tbl2sub_bias )[2]] %>%
kable( caption = .batch.labels[ 5 ], row.names = FALSE, 
       col.names = .col.names.b2, align = .align.b2, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b2, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b2 ) %>%
  add_header_above( .header.analysis.method.b2 )
```

\newpage
```{r batch-2-subset-power-table, cache = TRUE, echo = FALSE, results='asis'}
tbl2sub_power[, -dim( tbl2sub_power )[2]] %>%
kable( caption = .batch.labels[ 6 ], row.names = FALSE, 
       col.names = .col.names.b2, align = .align.b2, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b2, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b2 ) %>%
  add_header_above( .header.analysis.method.b2 )
```

\newpage
## Batch 3: Continuous outcome (Y), binary prognostic factors (X) {-}
```{r batch-3-table-settings, cache = TRUE, echo = FALSE, results = 'asis'}
.col.names.b3 = c("n", "exp( bZ )", "exp( bX )", "Pr( X )", "adj", "unadj", "adj", "unadj", "adj", "unadj", "adj");
.align.b3 = c(rep("c", 4), rep("r", 6), "c");
.latex_options.b3 = c("striped", "bordered", "hold_position")
.header.randomization.method.b3 = c(" " = 4, "CR" = 2, "SBR" = 2, "CAA" = 2, "CAA" = 1);
.header.analysis.method.b3 = c(" " = 4, "Model-based" = 6, "Rerandomization" = 1);

.batch.labels <- paste0("Table ", 3, c("a", "b", "c", "d", "e", "f"), 
                        ": (Continuous Y, binary X) ",
                        c("Coverage probability", "Bias", "Power"))
.linesep = kable_booktabs_linesep( nlines = 6 )
```

```{r batch-3-coverage-table, cache = TRUE, echo = FALSE, results='asis'}
tbl3_coverage[, -dim( tbl3_coverage )[2]] %>%
kable( caption = .batch.labels[ 1 ], row.names = FALSE, 
       col.names = .col.names.b3, align = .align.b3, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b3, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b3 ) %>%
  add_header_above( .header.analysis.method.b3 )
```

\newpage
```{r batch-3-bias-table, cache = TRUE, echo = FALSE, results='asis'}
tbl3_bias[, -dim( tbl3_bias )[2]] %>%
kable( caption = .batch.labels[ 2 ], row.names = FALSE, 
       col.names = .col.names.b3, align = .align.b3, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b3, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b3 ) %>%
  add_header_above( .header.analysis.method.b3 )
```

\newpage
```{r batch-3-power-table, cache = TRUE, echo = FALSE, results='asis'}
tbl3_power[, -dim( tbl3_power )[2]] %>%
kable( caption = .batch.labels[ 3 ], row.names = FALSE, 
       col.names = .col.names.b3, align = .align.b3, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b3, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b3 ) %>%
  add_header_above( .header.analysis.method.b3 )
```

\newpage
## Batch 4: Continuous outcome (Y), continuous prognostic factors (X) {-}
```{r batch-4-table-settings, cache = TRUE, echo = FALSE, results = 'asis'}
.col.names.b4 = c("n", "exp( bZ )", "exp( bX )", "adj", "unadj", "adj", "unadj", "adj", "unadj", "adj");
.align.b4 = c(rep("c", 3), rep("r", 6), "c");
.latex_options.b4 = c("striped", "bordered", "hold_position");
.header.randomization.method.b4 = c(" " = 3, "CR" = 2, "SBR" = 2, "CAA" = 2, "CAA" = 1);
.header.analysis.method.b4 = c(" " = 3, "Model-based" = 6, "Rerandomization" = 1);

.batch.labels <- paste0("Table ", 4, c("a", "b", "c", "d", "e", "f"), 
                        ": (Continuous Y, continuous X) ",
                        c("Coverage probability", "Bias", "Power"))
.linesep = kable_booktabs_linesep( nlines = 6 )
```

```{r batch-4-coverage-table, cache = TRUE, echo = FALSE, results='asis'}
tbl4_coverage[, -dim( tbl4_coverage )[2]] %>%
kable( caption = .batch.labels[ 1 ], row.names = FALSE, 
       col.names = .col.names.b4, align = .align.b4, booktabs = TRUE, linesep = .linesep ) %>%
  kable_styling( latex_options = .latex_options.b4, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b4 ) %>%
  add_header_above( .header.analysis.method.b4 )
```

\newpage
```{r batch-4-bias-table, cache = TRUE, echo = FALSE, results='asis'}
tbl4_bias[, -dim( tbl4_bias )[2]] %>%
kable( caption = .batch.labels[ 2 ], row.names = FALSE, 
       col.names = .col.names.b4, align = .align.b4, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b4, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b4 ) %>%
  add_header_above( .header.analysis.method.b4 )
```

\newpage
```{r batch-4-power-table, cache = TRUE, echo = FALSE, results='asis'}
tbl4_power[, -dim( tbl4_power )[2]] %>%
kable( caption = .batch.labels[ 3 ], row.names = FALSE, 
       col.names = .col.names.b4, align = .align.b4, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b4, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b4 ) %>%
  add_header_above( .header.analysis.method.b4 )
```

